Synpotic Soil Characterization

### 2024-11-11 3-reports/manuscript_figures.Rmd
updated scaled plot

>>>>

```{r v2-scaled_gg2_split-NEW, fig.height = 10, fig.width = 14}
library(ggh4x) # for nested facets
# https://teunbrand.github.io/ggh4x/reference/facet_nested.html

data_scaled_NEW2 = 
  data_scaled_NEW %>% 
  filter(name %in% c("WEOC", "TS", "Na", "Chloride", "Fe", "P")) %>% 
    mutate(name = factor(name, levels = c("TC", "TS", "WEOC",
                                        "Ca", "Na", "Chloride",
                                        "NH4N", "Fe", "P")))

data_scaled_NEW2 %>% 
  ggplot(aes(x = transect, y = value_scaled, group = site, color = site))+
  geom_line(linewidth = 1) + geom_point(size = 4, aes(shape = site, fill = site), color = "black")+
#  facet_wrap( ~ name)+
  facet_nested_wrap(~ name + region, ncol = 4,
                    nest_line = element_line(colour = "grey"))+ 
  scale_color_manual(breaks = c("CRC", "PTR", "OWC",
                                "GCW", "MSM", "GWI"),
                     values = c("#d73027", "#fc8d59", "#fdbb84", 
                                "#74a9cf", "#2b8cbe", "#045a8d"))+
    scale_fill_manual(breaks = c("CRC", "PTR", "OWC",
                                "GCW", "MSM", "GWI"),
                     values = c("#d73027", "#fc8d59", "#fdbb84", 
                                "#74a9cf", "#2b8cbe", "#045a8d"))+
  scale_shape_manual(breaks = c("CRC", "PTR", "OWC",
                                "GCW", "MSM", "GWI"),
                     values = c(21, 23, 24, 21, 23, 24))+
  scale_x_discrete(labels = c("U", "T" , "W" ))+
  labs(x = "Transect", y = "Normalized concentration")+
  theme_kp()+
  theme(axis.text.y = element_blank(),
        panel.grid = element_blank())
